Grammar-Based Concept Alignment for Domain-Specific Machine Translation

### 2021-07-02 paper/paper.tex
example multiwords

\subsection{MT experiments} \label{mtexp}
% genereral idea behind MT experiments
The second set of experiments has the objective of assessing the quality of the final output of the system we propose: GF translation lexica. 
Because we are now focusing on using CA in the context of domain-specific MT, we do not make use of the PUD treebanks, where sentences come from a variety of different sources, but just of the course plans corpora. 
We do not construct a grammar specific to such domain: for small-scale MT experiments, it is sufficient to extend the extraction grammar itself with preexisting syntax rules defined in the RGL.

>>>>

% qualitative analysis: multiwords
Our system is, on the other hand, capable of extracting multiword alignments that are unlikely to be identified by a statistical tool, especially in the case of such a small dataset. Examples of this are the noun phrases  $\langle$\textit{the aim of the course, l'obiettivo del corso, syftet med kursen}$\rangle$ (a concept found in both corpora and, as such, trilingual), $\langle$\textit{Natural Language Processing, språkteknologi}$\rangle$ and $\langle$\textit{object oriented programming, programmazione ad oggetti}$\rangle$.

\subsection{MT experiments} \label{mtexp}
% general idea behind MT experiments
The second set of experiments has the objective of assessing the quality of the final output of the system we propose: GF translation lexica. 
Because we are now focusing on using CA in the context of domain-specific MT, we do not make use of the PUD treebanks, where sentences come from a variety of different sources, but just of the course plans corpora. 
We do not construct a grammar specific to such domain: for small-scale MT experiments, it is sufficient to extend the extraction grammar itself with preexisting syntax rules defined in the RGL.
